Long groovy title goes here

### 2013-07-06 shanghai.tex
I added a section called Functorial Properties of the Main Isomorphism.
Added a section based on our conversation at the Hua Ting Hotel, So
far, it just has place holders for the results we talked about, without
proofs. The first result I think I can prove without too much
difficulty. The rest is still under construction.

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\Weil}{W}
\newcommand{\Frob}{{\operatorname{Fr}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}

@@

>>>>

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\Weil}{W}
\newcommand{\Frob}{{\operatorname{Fr}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}

@@

\section{Functorial properties of the main isomorphism}

We have already seen that the trace of Frobenius defines a canonical isomorphism 
$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
In this section we expand on the canonicity of this group isomorphism 
by showing that it is a natural transformation. We also show

\begin{proposition}
The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
is a natural transformation between the following two contravariant functors 
from the category of algebraic tori over $K$ to the category of abelian groups: 
\begin{enumerate}
\item $T \mapsto \CSiso{\GN{T}}$
\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
\end{enumerate}
\end{proposition}

\Clifton{I think I can prove this proposition without too much difficulty.}
\begin{proof}
\end{proof}

\begin{proposition}
Let $K'/K$ be a finite Galois extension and let $T'$ be an algebraic torus over $K'$... 
\Clifton{This next part is very much under construction.}
The functor $\CS(\GN{T}) \to \CS(\GN{T}')$ defined above induces a group homomorphism 
that commutes, through trace of Frobenius, with ...
\[
\xymatrix{
\CS(\GN{T}) \ar[d] & \CSiso{\GN{T}} \ar[r]^{t_T} \ar[d] & \Hom_\text{ad}(T(K),\EEx) \ar[d] \\
\CS(\GN{T}') & \CSiso{\GN{T}'} \ar[r]^{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)\\
}
\]
\end{proposition}

\begin{proof}
\end{proof}
